### 2015-07-14 zplus.tex
Squash some commas.

% Extended this to address [[file:todo.txt::*Review%203:%20Limitation%20to%20three%20classes][Review 3: Limitation to three classes]]
\mifd's assessment ranks hypotheses as either
\emph{likely}, \emph{plausible} or \emph{unlikely}. A hypothesis $h$,
conditioned on evidence $\omega$,
is \emph{likely} if
$\kappa(h|\omega) < \kappa(\neg h|\omega)$, \emph{plausible} if $\kappa(h|\omega) = \kappa(\neg h|\omega)$
and \emph{unlikely} otherwise.
That is, a hypothesis is likely (unlikely) if some maximally likely scenario labels it as
true (false) , and no maximally likely scenario labels it as false (true).  A
hypothesis is plausible, in any other situation.
Note that this restriction to three classes applies to \mifd's output,
not its inputs --- the \tkappa\ values of \mifd's underlying model
range over arbitrary natural numbers as needed to distinguish
qualitatively distinct likelihoods.
It would be possible to alter the assessment process to provide more classes of
likelihood, using the difference in kappa ranks between the maximally likely
scenario in which a hypothesis is labeled as true (false) and the one in which
it is labeled as false (true).  We have not seen the need to do so and, indeed,
worry that additional precision would come at the cost of validity.

>>>>

% Extended this to address [[file:todo.txt::*Review%203:%20Limitation%20to%20three%20classes][Review 3: Limitation to three classes]]
\mifd's assessment ranks hypotheses as either
\emph{likely}, \emph{plausible} or \emph{unlikely}. A hypothesis $h$,
conditioned on evidence $\omega$,
is \emph{likely} if
$\kappa(h|\omega) < \kappa(\neg h|\omega)$, \emph{plausible} if $\kappa(h|\omega) = \kappa(\neg h|\omega)$
and \emph{unlikely} otherwise.
That is, a hypothesis is likely (unlikely) if some maximally likely scenario labels it as
true (false), and no maximally likely scenario labels it as false (true).  A
hypothesis is plausible in any other situation.
Note that this restriction to three classes applies to \mifd's output,
not its inputs --- the \tkappa\ values of \mifd's underlying model
range over arbitrary natural numbers as needed to distinguish
qualitatively distinct likelihoods.
It would be possible to alter the assessment process to provide more classes of
likelihood, using the difference in kappa ranks between the maximally likely
scenario in which a hypothesis is labeled as true (false) and the one in which
it is labeled as false (true).  We have not seen the need to do so, and indeed
worry that additional precision would come at the cost of validity.
